---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
  knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%"
)
```

# `{chatRAG}`

<!-- badges: start -->
<!-- badges: end -->

{chatRAG} is a demo Retrieval Augmented Generation (RAG) Shiny app.  It is not intended for production use (although it may be suitable as a starting point). Its intended purpose is as a demonstrator to help make RAG more approachable and understandable as a technology to those who may commission and use RAG projects built by analysts and developers.

## Installation

You can install the development version of `{chatRAG}` like so:

```{r, eval=FALSE}
#install.packages("pak")
pak::pkg_install("ThomUK/chatRAG")
```

## Run

You can launch the application by running:

```{r, eval = FALSE}
chatRAG::run_app()
```

## About

You are reading the doc about version : `r golem::pkg_version()`

This README has been compiled on the

```{r}
Sys.time()
```

Here are the tests results and package coverage:

```{r, error = TRUE}
devtools::check(quiet = TRUE)
```

```{r echo = FALSE}
unloadNamespace("chatRAG")
```

```{r, error = TRUE}
covr::package_coverage()
```
